Finite-state morphological transducers for three Kypchak languages

### 2014-03-22 kipchak-lrec-2013/kipchak-paper.tex
try this for graphics position
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51102 72bbbca6-d526-0410-a7d9-f06f51895060
update
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51103 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{figure}
%\centering
\hspace{-35pt}
    \rotatebox{-90}{
\includegraphics[width=0.38\textwidth]{graphs/kumyk-yoldash-coverage}
}
~\\
~\\

@@

%FIXME: footnote with urls
This list of surface forms was then analysed with the most recent version of the analyser, and each analysis was checked.  Where an analysis was erroneous, it was removed; where an analysis was missing, it was added.  This process gave us a `gold standard' morphologically analysed word list of 1,000 surface forms with their analyses.  The list is publically available for each language.%\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/branches/apertium-kir/eval/ref.1000.txt}}

@@

@@

The authors would also like to express their gratitude to Aida Sundetova 
%and Ağarhim Sultanmuradov
for assistance in evaluating precision and recall.

>>>>

\begin{figure}
\centering
%\hspace{-35pt}
    \rotatebox{-90}{
\includegraphics[width=0.38\textwidth,bb=0 50 554 770]{graphs/kumyk-yoldash-coverage}
}
%~\\
%~\\

@@

%FIXME: footnote with urls
This list of surface forms was then analysed with the most recent version of the analyser, and each analysis was checked.  Where an analysis was erroneous, it was removed; where an analysis was missing, it was added.  This process gave us a `gold standard' morphologically analysed word list of 1,000 (Kazakh and Tatar) and 500 (Kumyk) surface forms with their analyses.  The list is publically available for each language.%\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/branches/apertium-kir/eval/ref.1000.txt}}

The lower number of forms for Kumyk was due to the limited access to native speakers of Kumyk. 
The process for the Kumyk evaluation was also slightly different. They were first checked by a non-expert native speaker of Kumyk and then the result was proofread by the authors with the help of a dictionary.

@@

%Due to limited access to native Kumyk speakers, the authors performed precision themselves based on their admittedly incomplete knowledge of the language.  
Recall is low for Kumyk due mostly to some systematic gaps in the morphotactics, such as lack of attributive analyses in several continuation lexica. There are also a higher number of missing verb stems (over half of all missing analyses were verb forms) in the Kumyk results than in the Kazakh and Tatar, where missing verb stems accounted for 10\% and 8\% respectively.

@@

The authors would also like to express their gratitude to Aida Sundetova 
and Ağarhim Sultanmuradov
for assistance in evaluating precision and recall.
